KidsAIR initial data work

### 2019-11-21 data_cleaning_initial.Rmd
pm data cleaning

```{r}

```

>>>>

```{r}
# Load Dusttrack data
## List sheets within the excel file
list_sheets_nm <- excel_sheets("Input/nm_kids_dusttrack_20191121.xlsx")
## Apply the read_xlsx function to each item in the sheet list
## Bind the items from each sheet into a single dataframe
pm_initial_nm <- data.frame(do.call("rbind", lapply(list_sheets_nm, read_xlsx, 
                                      path = "Input/nm_kids_dusttrack_20191121.xlsx")))

list_sheets_wmt <- excel_sheets("Input/wmt_kids_dusttrack_20191121.xlsx")
pm_initial_wmt <- data.frame(do.call("rbind", lapply(list_sheets_wmt, read_xlsx, 
                                      path = "Input/wmt_kids_dusttrack_20191121.xlsx")))

# Bind data together from different study areas
pm_initial <- rbind(pm_initial_nm, pm_initial_wmt)

# Rename and create new variables
kids_pm <- pm_initial %>% 
  separate(time, into = c("trash", "time"), sep = " ") %>% 
  mutate(id_home = as.factor(homeid),
         date = ymd(date),
         time = hms(time),
         pm25 = as.numeric(aerosol)) %>% 
  unite(datetime, c("date", "time"), sep = " ", remove = FALSE) %>% 
  mutate(datetime = ymd_hms(datetime)) %>% 
  select(id_home, date, time, datetime, pm25) %>% 
  arrange(id_home, date) %>% 
  group_by(id_home) %>% 
  mutate(obs = n(),
         total = sum(pm25),
         min_datetime = as.character(datetime),
         min_datetime = min(min_datetime)),
         max_datetime = as.character(datetime),
         max_datetime = max(max_datetime)),
         diff_datetime = ymd_hms(max_datetime) - ymd_hms(min_datetime))

test <- kids_pm %>% 
  group_by(id_home) %>% 
  summarize(n())
```
